Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-07-08 manuscript.Rmd
Updated annual change.

---
title: 'Examining a Quarter Century of Publishing Trends in Social Work Research:
  A Data Science Perspective'
author: ''
date: "May 26, 2015"
output: pdf_document
header-includes:
- \usepackage{indentfirst}
- \usepackage{setspace}
- \doublespacing
- \setlength{\parindent}{4em}
---

@@

>>>>

---
title: 'Examining a Quarter Century of Publishing Trends in Social Work Research:
  A Data Science Perspective'
author: ''
date: "May 26, 2015"
output: html_document
header-includes:
- \usepackage{indentfirst}
- \usepackage{setspace}
- \doublespacing
- \setlength{\parindent}{4em}
---

@@

```{r}
articles.df$YearRecode <- c(nrow(articles.df):1)
ggplot(articles.df, aes(Year, N)) +  
  geom_smooth(method="lm") + 
  geom_line() +
  geom_point()

options(digits = 4)
x <- lm(N ~ YearRecode, data = articles.df)
summary(x)

articlesN <- rev(articles.df$N)
articlesN <- ts(articlesN, frequency=1, start = 1989, end = 2013)
diff(articlesN)/articlesN[-nrow(articlesN),]*100

curr <- articles.df$N[-1]
prev <- articles.df$N[1:(length(articles.df$N)-1)]
articles.df <- arrange(articles.df, Year)
articles.df$monChange <- c(0, (100 *  (curr-prev) / prev)) 
articles.df <- mutate(articles.df, positiveNegative = as.factor(ifelse(articles.df$monChange >= 0, "Positive", "Negative")))

ggplot(articles.df, aes(Year, monChange, fill = positiveNegative)) + geom_bar(stat="identity") 
mean(articles.df$monChange[2:25])
